Model LF

### 2022-09-20 Estimation.Rmd
commit

```{r, message=FALSE}
AAMK <- read_excel("AAMK.xlsx")
globaldemand1 <- read_excel("globaldemand1.xlsx")
w_h_r1 <- read_excel("w_h_r1.xlsx")
emp1= ts(w_h_r1$emp1, start = c(2003,1), frequency = 4)
w_h_r1= ts(w_h_r1$w_h_r1, start = c(2003,1), frequency = 4)

@@

```{r}
#empl = N/1000
#empl_ds = Nadj/1000
 wage = w_h_r/emp
wage1= w_h_r1/emp1
# wage = w_h_rk_ds /(empl_ds)
 Nu=(w_row_r - w_row_p)/wage
 Nf = Nu + emp
 prod = y/Nf
 LF = unemp + emp
 lfadj = unempadj + empadj
 ur = unemp/LF
 ur_ds = unempadj/lfadj
# yk = y/(py/100)
 prodk = yk/Nf
 yf = w + b2
 ws = w/yf
 ps = 1 - ws
# w = w_h_r + (W_row_r - W_row_p)
 fdis = yf/y
 urterm = ur - urs
 wageindex = wage/wage[22] #element from 2010Q3
 priv = pconk + ik + xk
 part = LF*1000/pop
 old_age_ratio = retired_pop/pop
 part1= LF*1000/(pop*(1-old_age_ratio))
 zaland_jesper = pop - LF*1000  
 nben_h = nsben_h + d8_h
```

@@

```{r}
## Creating the new shock variables
g_shock= g*1.02
prodk_ds_shock = prodk_ds
max_dp_shock= obs_dp_q
stat_reg_shock = ts(0.02, start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

#### Shock variables 
shock_max_dp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_reg_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_part_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

#### Sensitivity analysis variables 
sens1=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

```{r}
mean_dp_wage= 0.9507*wage_dp_q
total_dp_wage= mean_dp_wage*unemp*kuld
komp_r_wage=mean_dp_wage/wage_trim1
```

```{r}
tilpas_pr = window(tilpas_pr_q, start= c(2006,1))
stat_tilpas = window(stat_tilpas_q, start= c(2006,1))
stat_reg = window(stat_reg_q, start= c(2006,1))
```

```{r}
max_dp_test= TSLAG(obs_dp_q,4) +(stat_reg_q+stat_tilpas_q) * TSLAG(obs_dp_q,4) 
```

@@

@@

COMMENT> Max_dp

COMMENT> Lavet for at kunne støde til g 
IDENTITY> max_dp
EQ> max_dp = TSLAG(max_dp,4)+ (stat_reg+stat_tilpas)*TSLAG(max_dp,4)
IF> shock_max_dp_model <= 0 & SD1 >= 1
IDENTITY> max_dp
EQ> max_dp = TSLAG(max_dp,1)
IF>  SD2 >= 1
IDENTITY> max_dp
EQ> max_dp = TSLAG(max_dp,2)
IF>  SD3 >= 1
IDENTITY> max_dp
EQ> max_dp = TSLAG(max_dp,3)
IF>  SD4 >= 1
IDENTITY> max_dp
EQ> max_dp = TSLAG(max_dp,4)+ TSDELTA(TSLAG(wage,8),4)/TSLAG(wage,12)*TSLAG(max_dp,4)
IF> shock_max_dp_model > 0 & SD1 >= 1

COMMENT>  
IDENTITY> stat_tilpas
EQ> stat_tilpas = tilpas_pr
IF> tilpas_pr < 0 & SD1 >= 1
IDENTITY> stat_tilpas
EQ> stat_tilpas = 0
IF> tilpas_pr >= 0 & tilpas_pr <=0.003 & SD1 >= 1
IDENTITY> stat_tilpas
EQ> stat_tilpas = tilpas_pr - 0.003
IF> tilpas_pr >=0.003 & SD1 >= 1
IDENTITY> stat_tilpas
EQ> stat_tilpas = TSLAG(stat_tilpas,1)
IF>  SD2 >= 1
IDENTITY> stat_tilpas
EQ> stat_tilpas = TSLAG(stat_tilpas,2)
IF>  SD3 >= 1
IDENTITY> stat_tilpas
EQ> stat_tilpas = TSLAG(stat_tilpas,3)
IF>  SD4 >= 1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> tilpas_pr
EQ> tilpas_pr = TSDELTA(TSLAG(wage,8),4)/TSLAG(wage,12) - 0.02
IF>  SD1 >= 1
IDENTITY> tilpas_pr
EQ> tilpas_pr = TSLAG(tilpas_pr,1)
IF>  SD2 >= 1
IDENTITY> tilpas_pr
EQ> tilpas_pr = TSLAG(tilpas_pr,2)
IF>  SD3 >= 1
IDENTITY> tilpas_pr
EQ> tilpas_pr = TSLAG(tilpas_pr,3)
IF>  SD4 >= 1

@@

COMMENT> tilføjet
IDENTITY> dp_person
EQ>  dp_person = 0.9507*max_dp
IF>  sens1 <= 0
IDENTITY> dp_person
EQ> dp_person = 0.85*max_dp
IF>  sens1 >= 1

COMMENT> Sensitivitets analyse
IDENTITY> sens1
EQ> sens1 = sens1*1

@@

COMMENT> Mangler stadig at få tilpasset til ik diff
BEHAVIORAL> l_h_tr_ratio
TSRANGE 2006 2 2020 1
EQ> TSDELTA(l_h_tr_ratio) = p_646 
+ p_641*TSDELTA(TSLAG(l_h_tr_ratio,2))
+ p_642*TSDELTA(iloan) 
+ p_643*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(yd_hk_ds,3)) 
+ p_644* TSLAG(l_h_tr_ratio,1) 
+ p_645*LOG(TSLAG(-l_h,2)/(TSLAG(yd_hk_ds,2)*TSLAG(pc,2)))
+ p_647*d_2007q34 
+ p_648*time
COEFF> p_646 p_641 p_642 p_643 p_644 p_645 p_647 p_648
STORE>  coe(5)

@@

COMMENT> 
IDENTITY> lf
EQ> lf = (part*pop)/1000
IF> shock_part_model <=0
IDENTITY> lf
EQ> lf = (part1*pop*(1-old_age_ratio))/1000
IF> shock_part_model > 0

@@

COMMENT> 
IDENTITY> inflation_t
EQ> inflation_t = inflation_tt
IF> inflation_tt <= 0
IDENTITY> inflation_t
EQ> inflation_t = inflation
IF> inflation_tt > 0

@@

IDENTITY> part
EQ> part = part*1
IF> shock_part_model <= 0
IDENTITY> part
EQ> part = lf*1000/pop
IF> shock_part_model > 0

BEHAVIORAL> part1
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(part1) = beta_0 + beta_1*TSDELTALOG(TSLAG(part,2)) + beta_2*TSDELTALOG(TSLAG(part,4)) + beta_3*TSDELTALOG(komp_r) + beta_4*TSDELTALOG(TSLAG(komp_r,3)) +beta_5*TSDELTALOG(rw_ds) + beta_6*TSDELTALOG(TSLAG(rw_ds,1)) + beta_7*TSDELTA(TSLAG(ur_ds,3)) + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(komp_r,1)) + beta_11*TSLAG(ur_ds,1) + beta_12* d_2013q4
COEFF> beta_0 beta_1 beta_2 beta_3 beta_4 beta_5 beta_6 beta_7 beta_8 beta_9 beta_10 beta_11 beta_12
STORE> coe(16)

@@

COMMENT> Capital Stock with switches
IDENTITY> stat_reg
EQ> stat_reg = stat_reg*1
IF> shock_reg_model <= 0
IDENTITY> stat_reg
EQ> stat_reg = stat_reg_shock
IF> shock_reg_model > 0

@@

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_reg_model
EQ> shock_reg_model = shock_reg_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_max_dp_model
EQ> shock_max_dp_model = shock_max_dp_model*1

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_part_model
EQ> shock_part_model = shock_part_model*1

@@

  ##Sensitivites analyse

   sens1 = TIMESERIES(c(sens1),   
                       START=c(2006,1),FREQ=4),

  ## max_dp

  stat_reg = TIMESERIES(c(stat_reg),   
                       START=c(2006,1),FREQ=4),
  stat_tilpas = TIMESERIES(c(stat_tilpas),   
                       START=c(2006,1),FREQ=4),
  tilpas_pr = TIMESERIES(c(tilpas_pr),   
                       START=c(2006,1),FREQ=4),

  ## Price adjustments
  pg_adj = TIMESERIES(c(pg_adj),   
                       START=c(2005,2),FREQ=4),
  p_bd_adj = TIMESERIES(c(p_bd_adj),   
                       START=c(2005,2),FREQ=4),
  p_equip_adj = TIMESERIES(c(p_equip_adj),   
                     START=c(2005,2),FREQ=4),
  px_adj = TIMESERIES(c(px_adj),   
                        START=c(2005,2),FREQ=4),
  ## Households

  max_dp_shock = TIMESERIES(c(max_dp_shock),   
                       START=c(2005,2),FREQ=4),
  part1 = TIMESERIES(c(part1),   
                       START=c(2005,2),FREQ=4),

@@

  rw_ds = TIMESERIES(c(rw_ds),   
                     START=c(2005,2),FREQ=4),
  wage = TIMESERIES(c(wage1),   
                    START=c(2003,1),FREQ=4),

@@

   nben_h_rest = TIMESERIES(c(nben_h_rest_obs),   
                       START=c(2005,2),FREQ=4),
  nben_h_un = TIMESERIES(c(nben_h_un_obs),   
                        START=c(2005,2),FREQ=4),
  komp_r = TIMESERIES(c(komp_r_obs),   
                        START=c(2005,2),FREQ=4),
  shock = TIMESERIES(c(shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  stat_reg_shock = TIMESERIES(c(stat_reg_shock),   
                        START=c(2005,2),FREQ=4),

@@

   shock_reg_model  = TIMESERIES(c(shock_reg_model ),   
                           START=c(2005,2),FREQ=4),

   shock_g_model  = TIMESERIES(c(shock_g_model ),   
                           START=c(2005,2),FREQ=4),
  shock_max_dp_model  = TIMESERIES(c(shock_max_dp_model ),   
                           START=c(2005,2),FREQ=4),
  shock_part_model  = TIMESERIES(c(shock_part_model ),   
                           START=c(2005,2),FREQ=4),

@@

```{r, echo=FALSE}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr

yk_ds_00 = S_model$simulation$yk_ds
part_00 = S_model$simulation$part
lf_00 = S_model$simulation$lf
pconk_ds_00 = S_model$simulation$pconk_ds
yd_h1_00 = S_model$simulation$yd_h1 
nben_h_rest_00 = S_model$simulation$nben_h_rest
nben_h_un_00 = S_model$simulation$nben_h_un
komp_r_00 = S_model$simulation$komp_r
nben_h_00 = S_model$simulation$nben_h
wageindex_00 = S_model$simulation$wageindex
yh1_00 = S_model$simulation$yh1
yd1_h_00 = S_model$simulation$yd1_h
yd_hk_00 = S_model$simulation$yd_hk
yd_h_00 = S_model$simulation$yd_h
l_h_tr_00 = S_model$simulation$l_h_tr
s_h_00 = S_model$simulation$s_h
eq_h_00 = S_model$simulation$eq_h
iba_h_00 = S_model$simulation$iba_h
yd1_hk_ds_00 = S_model$simulation$yd1_hk_ds
ur_00 = S_model$simulation$ur
ur_ds_00 = S_model$simulation$ur_ds
iba_f_tr_00 = S_model$simulation$iba_f_tr
iba_h_tr_00 = S_model$simulation$iba_h_tr
iba_nf_tr_00 = S_model$simulation$iba_nf_tr
nl_nf_00 = S_model$simulation$nl_nf
neq_nf_tr_00 = S_model$simulation$neq_nf_tr
l_nf_tr_00 = S_model$simulation$l_nf_tr
sec_nf_tr_00 = S_model$simulation$sec_nf_tr
ins_nf_tr_00 = S_model$simulation$ins_nf_tr
neq_nf_00 = S_model$simulation$neq_nf
i_nf_00 = S_model$simulation$i_nf
np_nf_00 = S_model$simulation$np_nf
s_nf_00 = S_model$simulation$s_nf
yh_nf_00 = S_model$simulation$yh_nf
y_00 = S_model$simulation$y
b2_nf_r_00 = S_model$simulation$b2_nf_r
p_tax_00 = S_model$simulation$p_tax
b2_00 = S_model$simulation$b2
w_nf_00 = S_model$simulation$w_nf
npropinc_nf_00 = S_model$simulation$npropinc_nf
int_nf_00 = S_model$simulation$int_nf
div_nf_00 = S_model$simulation$div_nf
eq_nf_a_f_00 = S_model$simulation$eq_nf_a_f
eq_nf_l_nf_00 = S_model$simulation$eq_nf_l_nf
eq_nf_a_nf_00 = S_model$simulation$eq_nf_a_nf
eq_h_nf_00 = S_model$simulation$eq_h_nf
eq_row_a_nf_00 = S_model$simulation$eq_row_a_nf
eq_f_a_nf_00 = S_model$simulation$eq_f_a_nf
eq_g_nf_00 = S_model$simulation$eq_g_nf
eq_nf_a_row_00 = S_model$simulation$eq_nf_a_row
neq_nf_00 = S_model$simulation$neq_nf
check_div_00 = S_model$simulation$check_div
xk_ds_00 = S_model$simulation$xk_ds
g_00 = S_model$simulation$g
rw_ds_00 = S_model$simulation$rw_ds
b2_00 = S_model$simulation$b2
test = S_model$simulation$test

@@

sens1_00 = S_model$simulation$sens1

part1_00 = S_model$simulation$part1
```

# Tjek

```{r}
plot(tilpas_pr_00, col= "green"); lines(tilpas_pr, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(wage_trim_00, col= "green"); lines(wage_trim1, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

plot(stat_tilpas_00, col= "green", ylim= c(-0.03,0.05)); lines(stat_tilpas, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(max_dp_00, col= "green"); lines(obs_dp_q, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(wage_00, col= "green"); lines(wage, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

Plots for paper

```{r, fig.width=12, fig.height=7}
par(mfrow=c(1,2))

plot(yk_ds_00, col= "red"); lines(yk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(emp_00, col= "red"); lines(emp, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

```{r, fig.width=12, fig.height=7}
par(mfrow=c(1,2))

plot(max_dp_00, col= "red"); lines(obs_dp_q, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_00, col= "red"); lines(komp_r_obs, col = "blue"); 
legend("top",legend=c("Baseline", "Data"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

## Scenario 1 max_dp

```{r}
shock_max_dp_model_shock=shock_max_dp_model %>% window(start= c(2006,3))
```

@@

 shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

@@

```{r}
###Gengivelse af stød til model
max_dp_01 = Shock_1$simulation$max_dp
wage_01 = Shock_1$simulation$wage
komp_r_01 = Shock_1$simulation$komp_r
part_01 = Shock_1$simulation$part
yk_ds_01 = Shock_1$simulation$yk_ds
pc_ds_01 = Shock_1$simulation$pc_ds
emp_01 = Shock_1$simulation$emp
ur_ds_01 = Shock_1$simulation$ur_ds

yd_h1_01 = Shock_1$simulation$yd_h1

w_h_r_01 = Shock_1$simulation$w_h_r

wage_ds_01 = Shock_1$simulation$wage_ds

yd_g_01 = Shock_1$simulation$yd_g

nben_h_01 = Shock_1$simulation$nben_h
```

@@

plot(max_dp_01, col= "red"); lines(max_dp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_01, col= "red"); lines(wage_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(komp_r_01, col= "red"); lines(komp_r_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(part_01, col= "red"); lines(part_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

plot(nben_h_01, col= "red"); lines(nben_h_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

Plots for paper:

```{r}
par(mfrow=c(1,2))

plot(emp_01, col= "red"); lines(emp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

## Scenario 1 reg

```{r}
shock_reg_model_shock=shock_reg_model %>% window(start= c(2016,1))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList1 <- list(

 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q')

@@

```{r}
# Simulate the model (following shock)
Shock_1b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1
                    )
```

>>>>

```{r, message=FALSE}
AAMK <- read_excel("AAMK.xlsx")
globaldemand1 <- read_excel("globaldemand1.xlsx")

@@

```{r}
#empl = N/1000
#empl_ds = Nadj/1000
 wage = w_h_r/emp
# wage = w_h_rk_ds /(empl_ds)
 Nu=(w_row_r - w_row_p)/wage
 Nf = Nu + emp
 prod = y/Nf
 LF = unemp + emp
 lfadj = unempadj + empadj
 ur = unemp/LF
 ur_ds = unempadj/lfadj
# yk = y/(py/100)
 prodk = yk/Nf
 yf = w + b2
 ws = w/yf
 ps = 1 - ws
# w = w_h_r + (W_row_r - W_row_p)
 fdis = yf/y
 urterm = ur - urs
 wageindex = wage/wage[22] #element from 2010Q3
 priv = pconk + ik + xk
 part = LF*1000/pop
 old_age_ratio = retired_pop/pop
 zaland_jesper = pop - LF*1000  
 nben_h = nsben_h + d8_h
```

@@

```{r}
## Creating the new shock variables
g_shock= g*1.02
prodk_ds_shock = prodk_ds
max_dp_shock= obs_dp_q

@@

#### Shock variables 
shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

```{r}
mean_dp_wage= 0.9507*wage_dp_q
total_dp_wage= mean_dp_wage*unemp*kuld
komp_r_wage=mean_dp_wage/wage_trim1

@@

## model

@@

@@

COMMENT> tilføjet
IDENTITY> dp_person
EQ>  dp_person = 0.9507*max_dp

@@

COMMENT> Mangler stadig at få tilpasset til ik diff
BEHAVIORAL> l_h_tr_ratio
TSRANGE 2006 2 2020 1
EQ> TSDELTA(l_h_tr_ratio) = p_646 
+ p_641*TSDELTA(TSLAG(l_h_tr_ratio,2))
+ p_642*TSDELTA(iloan) 
+ p_643*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(yd_hk_ds,3)) 
+ p_644* TSLAG(l_h_tr_ratio,1) 
+ p_645*LOG(TSLAG(-l_h,2)/TSLAG(yd_hk_ds,2)*TSLAG(pc,2)) 
+ p_647*d_2007q34 
+ p_648*time
COEFF> p_646 p_641 p_642 p_643 p_644 p_645 p_647 p_648
STORE>  coe(5)

@@

COMMENT> 
IDENTITY> lf
EQ> lf = (part*pop)/1000

@@

COMMENT> Capital Stock with switches
IDENTITY> inflation_t
EQ> inflation_t = inflation_tt
IF> inflation_tt <= 0
IDENTITY> inflation_t
EQ> inflation_t = inflation
IF> inflation_tt > 0

@@

COMMENT> Endogonize partitipation rate
BEHAVIORAL> part
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(part) = beta_0 + beta_1*TSDELTALOG(TSLAG(part,2)) + beta_2*TSDELTALOG(TSLAG(rw_ds,1)) + beta_3*TSDELTALOG(komp_r) + beta_4*TSDELTALOG(TSLAG(komp_r,3))  + beta_6*LOG(TSLAG(part,1))  + beta_7*log(TSLAG(rw_ds,1)) + beta_8*TSLAG(ur_ds,1) + beta_9* d_2013q4
COEFF> beta_0 beta_1 beta_2 beta_3 beta_4 beta_6 beta_7 beta_8 beta_9
STORE> coe(16)

COMMENT> Lavet for at kunne støde til g 
IDENTITY> max_dp
EQ> max_dp = max_dp_shock

@@

@@

@@

  ## Price adjustments
  pg_adj = TIMESERIES(c(pg_adj),   
                       START=c(2005,2),FREQ=4),
  p_bd_adj = TIMESERIES(c(p_bd_adj),   
                       START=c(2005,2),FREQ=4),
  p_equip_adj = TIMESERIES(c(p_equip_adj),   
                     START=c(2005,3),FREQ=4),
  px_adj = TIMESERIES(c(px_adj),   
                        START=c(2005,2),FREQ=4),
  ## Households

  max_dp_shock = TIMESERIES(c(max_dp_shock),   
                       START=c(2005,2),FREQ=4),

@@

  rw_ds = TIMESERIES(c(rw_ds),   
                     START=c(2005,2),FREQ=4),
  wage = TIMESERIES(c(wage),   
                    START=c(2005,2),FREQ=4),

@@

   nben_h_rest = TIMESERIES(c(nben_h_rest_obs),   
                       START=c(2005,2),FREQ=4),
  nben_h_un = TIMESERIES(c(nben_h_un_obs),   
                        START=c(2005,2),FREQ=4),
  komp_r = TIMESERIES(c(komp_r_obs),   
                        START=c(2005,2),FREQ=4),
  shock = TIMESERIES(c(shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),

@@

   shock_g_model  = TIMESERIES(c(shock_g_model ),   
                           START=c(2005,2),FREQ=4),

@@

```{r, echo=FALSE}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp

part_00 = S_model$simulation$part
lf_00 = S_model$simulation$lf
pconk_ds_00 = S_model$simulation$pconk_ds
yd_h1_00 = S_model$simulation$yd_h1 
nben_h_rest_00 = S_model$simulation$nben_h_rest
nben_h_un_00 = S_model$simulation$nben_h_un
komp_r_00 = S_model$simulation$komp_r
nben_h_00 = S_model$simulation$nben_h
wageindex_00 = S_model$simulation$wageindex
yh1_00 = S_model$simulation$yh1
yd1_h_00 = S_model$simulation$yd1_h
yd_hk_00 = S_model$simulation$yd_hk
yd_h_00 = S_model$simulation$yd_h
l_h_tr_00 = S_model$simulation$l_h_tr
s_h_00 = S_model$simulation$s_h
eq_h_00 = S_model$simulation$eq_h
iba_h_00 = S_model$simulation$iba_h
yd1_hk_ds_00 = S_model$simulation$yd1_hk_ds
ur_00 = S_model$simulation$ur
ur_ds_00 = S_model$simulation$ur_ds
iba_f_tr_00 = S_model$simulation$iba_f_tr
iba_h_tr_00 = S_model$simulation$iba_h_tr
iba_nf_tr_00 = S_model$simulation$iba_nf_tr
nl_nf_00 = S_model$simulation$nl_nf
neq_nf_tr_00 = S_model$simulation$neq_nf_tr
l_nf_tr_00 = S_model$simulation$l_nf_tr
sec_nf_tr_00 = S_model$simulation$sec_nf_tr
ins_nf_tr_00 = S_model$simulation$ins_nf_tr
neq_nf_00 = S_model$simulation$neq_nf
i_nf_00 = S_model$simulation$i_nf
np_nf_00 = S_model$simulation$np_nf
s_nf_00 = S_model$simulation$s_nf
yh_nf_00 = S_model$simulation$yh_nf
y_00 = S_model$simulation$y
b2_nf_r_00 = S_model$simulation$b2_nf_r
p_tax_00 = S_model$simulation$p_tax
b2_00 = S_model$simulation$b2
w_nf_00 = S_model$simulation$w_nf
npropinc_nf_00 = S_model$simulation$npropinc_nf
int_nf_00 = S_model$simulation$int_nf
div_nf_00 = S_model$simulation$div_nf
eq_nf_a_f_00 = S_model$simulation$eq_nf_a_f
eq_nf_l_nf_00 = S_model$simulation$eq_nf_l_nf
eq_nf_a_nf_00 = S_model$simulation$eq_nf_a_nf
eq_h_nf_00 = S_model$simulation$eq_h_nf
eq_row_a_nf_00 = S_model$simulation$eq_row_a_nf
eq_f_a_nf_00 = S_model$simulation$eq_f_a_nf
eq_g_nf_00 = S_model$simulation$eq_g_nf
eq_nf_a_row_00 = S_model$simulation$eq_nf_a_row
neq_nf_00 = S_model$simulation$neq_nf
check_div_00 = S_model$simulation$check_div
xk_ds_00 = S_model$simulation$xk_ds
g_00 = S_model$simulation$g
rw_ds_00 = S_model$simulation$rw_ds
b2_00 = S_model$simulation$b2
test = S_model$simulation$test

@@

```{r}
plot(wage_trim_00, col= "green"); lines(wage_trim1, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

plot(komp_r_00, col= "green"); lines(komp_r_obs, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

@@

## Scenario 3 g

```{r}
shock_g_model_shock=shock_g_model %>% window(start= c(2014,2))
```

@@

 shock_g_model = TIMESERIES(shock_g_model_shock+1 ,START=c(2014,2),  FREQ='Q')

@@

```{r}
# Simulate the model (following shock)
Shock_3 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList
                    )
```

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds

komp_r_03 = Shock_3$simulation$komp_r

plot(komp_r_03, col= "red"); lines(komp_r_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_03, col= "red"); lines(yk_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_03, col= "red"); lines(ur_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_03, col= "red"); lines(wage_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pconk_ds_03, col= "red"); lines(pconk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pc_ds_03, col= "red"); lines(pc_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yd_hk_ds_03, col= "red"); lines(yd_hk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

## Scenario 1

 shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q')

@@

yk_ds_01 = Shock_1$simulation$yk_ds
emp_01 = Shock_1$simulation$emp
wage_ds_01 = Shock_1$simulation$wage_ds
ur_ds_01 = Shock_1$simulation$ur_ds
pc_ds_01 = Shock_1$simulation$pc_ds
yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds
pconk_ds_01 = Shock_1$simulation$pconk_ds

@@

plot(ur_ds_01, col= "red"); lines(ur_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_01, col= "red"); lines(wage_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pconk_ds_01, col= "red"); lines(pconk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

plot(yd_hk_ds_01, col= "red"); lines(yd_hk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

## Scenario 2

```{r}
shock_iloan=iloan %>% window(start= c(2014,4))
shock_idep=idep %>% window(start= c(2014,4))
shock_ibd=ibd %>% window(start= c(2014,4))
shock_iboa=iboa %>% window(start= c(2014,4))

# Test

shock_2_model_shock=shock_2_model %>% window(start= c(2014,4))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_1 <- list(

  shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q'),
  shock_2_model = TIMESERIES(shock_2_model_shock+1 ,START=c(2014,4),  FREQ='Q')

@@

```{r}
# Simulate the model (following shock)
Shock_2 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_1
                    )
```

yk_ds_02 = Shock_2$simulation$yk_ds
emp_02 = Shock_2$simulation$emp
wage_ds_02 = Shock_2$simulation$wage_ds
ur_ds_02 = Shock_2$simulation$ur_ds
pc_ds_02 = Shock_2$simulation$pc_ds
yd_hk_ds_02 = Shock_2$simulation$yd_hk_ds
pconk_ds_02 = Shock_2$simulation$pconk_ds

## Scenario 4

```{r}
# Test

shock_3_model_shock=shock_3_model %>% window(start= c(2014,4))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_3 <- list(

   shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q'),
  shock_3_model = TIMESERIES(shock_3_model_shock+1 ,START=c(2014,4),  FREQ='Q')
